\documentclass[letterpaper]{report}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{titlesec,longtable}
\author{Nathan Harrenstein}
\title{Composer Timeline Design}

\renewcommand{\arraystretch}{1.75}

\titleformat{\section}{\normalfont\fontsize{11}{13.2}\bfseries}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{18pt plus 6pt minus 6pt}{18pt plus 6pt minus 6pt}

\begin{document}

\maketitle

\renewcommand{\baselinestretch}{1.25}\normalsize
\tableofcontents
\renewcommand{\baselinestretch}{1}\normalsize

\chapter{Introduction}

\chapter{Data}

\begin{longtable}{p{0.45\linewidth} p{0.05\linewidth} p{0.45\linewidth}}
What & When & Where \\ \hline
Performer.Name & Now & Used to reduce duplicate data between CompositionCollectionAudioFilePerformer.Performer, CompositionAudioFilePerformer.Performer, and MovementAudioFilePerformer.Performer. \\
Album.Name & Now & Used to reduce duplicate data between CompositionCollectionAudioFile.Album, CompositionAudioFile.Album, and MovementAudioFile.Album. \\
Location.Name & Now & Used to reduce duplicate data between Composer.BirthLocation, Composer.DeathLocation, CompositionCollectionAudioFile.RecordingLocation, CompositionAudioFile.RecordingLocation, and MovementAudioFile.RecordingLocation. \\
Era.Name & Now & Used to reduce duplicate data of Composer.Era. \\
Nationality.Name & Now & Used to reduce duplicate data of Composer.Nationality \\
CompositionCollection.CommonName & Now & Displayed in the composition list on the ComposerPage. \\
CompositionCollection.IsPopular & Now & Stars are set beside the names of popular composition collections. \\
Composer.CommonSortName & Now & Displayed on ComposerControls, ComposerPages, and in lists sortable by last name. \\
Composer.BirthYear & Now & Positions the composer along the timeline, and displayed in the ComposerPage and on ComposerControls. Only the year is required as the timeline is based around years. \\
Composer.DeathYear & Now & Positions the composer along the timeline, and displayed in the ComposerPage and on ComposerControls. Only the year is required as the timeline is based around years. \\
Composer.BirthPlace & Now & Displayed on ComposerControls and in the ComposerPage. \\
Composer.DeathPlace & Now & Displayed on ComposerControls and in the ComposerPage. \\
Composer.Nationality & Now & Identifies a composer's flag and is set as that flag's tooltip content. \\
Composer.Era & Now & Determines the color of the composer's ComposerControl. \\
Composer.Biography & Now & Displayed in the ComposerPage. \\
Composer.IsPopular & Now & Stars are set beside the names of popular composers. \\
Composition.CommonName & Now & Displayed in the composition list in the ComposerPage. \\
Composition.CompletionYear & Now & Appended to a composition name in the composition list in the ComposerPage when a composition does not have a catalog number. \\
Composition.Nickname & Now & Appended to a composition name in the composition list in the ComposerPage after the catalog number. \\
Composition.IsPopular & Now & A star is appended to a composition name in the composition list in the ComposerPage if the composition is popular. \\
CompositionCollectionAudioFile.Path & Now & Used to locate the audio file to play when clicking a composition collection in the composition list in the ComposerPage. \\
CompositionCollectionAudioFile.CompletionDate & Now & Used to distinguish audio files. \\
CompositionCollectionAudioFile.RecordingLocation & Now & Used to distinguish audio files. \\
CompositionCollectionAudioFile.Album & Now & Used to distinguish audio files. \\
CompositionCollectionAudioFile.TrackNumber & Now & Used to distinguish audio files. \\
CompositionCollectionAudioFilePerformer & Now & Used to link a performer to a composition collection audio file, which is then used to distinguish audio files. \\
CompositionAudioFile.Path & Now & Used to locate the audio file to play when clicking a composition collection in the composition list in the ComposerPage. \\
CompositionAudioFile.CompletionDate & Now & Used to distinguish audio files. \\
CompositionAudioFile.RecordingLocation & Now & Used to distinguish audio files. \\
CompositionAudioFile.Album & Now & Used to distinguish audio files. \\
CompositionAudioFile.TrackNumber & Now & Used to distinguish audio files. \\
Movement.CommonName & Now & Displayed in the composition list in the ComposerPage. \\
Movement.Number & Now & Displayed in the composition list in the ComposerPage. \\
Movement.IsPopular & Now & A star is appended to a movement name in the composition list in the ComposerPage if the movement is popular. \\
ComposerImage.Path & Now & Used to located ComposerImage files for display in the ComposerPage. \\
ComposerInfluence & Now & Used to link a composer to one of their influences or composers who have been influenced by that composer on the ComposerPage. \\
ComposerLink.URL & Now & Used to identify the web address pointed to by a link in the ComposerPage. \\
ComposerLink.FaviconPath & Now & Used to identify the cached favicon for a link in the ComposerPage. \\
CatalogNumberPrefix.Prefix & Now & Appended to a catalog number, which is then appended to a composition name in the composition list in the ComposerPage. \\
CompositionAudioFilePerformer & Now & Used to link a performer to a composition audio file, which is then used to distinguish audio files. \\
MovementAudioFile.Path & Now & Used to locate the audio file to play when clicking a composition collection in the composition list in the ComposerPage. \\
MovementAudioFile.CompletionDate & Now & Used to distinguish audio files. \\
MovementAudioFile.RecordingLocation & Now & Used to distinguish audio files. \\
MovementAudioFile.Album & Now & Used to distinguish audio files. \\
MovementAudioFile.TrackNumber & Now & Used to distinguish audio files. \\
CompositionCatalogNumber.Value & Now & Appended to a catalog number prefix, which is then appended to a composition name in the composition list in the ComposerPage. \\
CompositionCollectionCatalogNumber.Value & Now & Appended to a catalog number prefix, which is then appended to a composition collection name in the composition list in the ComposerPage. \\
MovementAudioFilePerformer & Now & Used to link a performer to a movement audio file, which is then used to distinguish audio files. \\
\end{longtable}

\end{document}